Computationally Efficient Simulation of Queues: The \proglang{R} Package \pkg{queuecomputer}

### 2020-07-17 jss3041.tex
Changed pdf
Changes before COVID-19

In the case of a $M/M/K$ system equilibrium distributions for performance measures are derived analytically, they are found in standard queueing theory textbooks \citep{lipsky2008queueing, thomopoulos2012fundamentals}. For instance, the limit probability of $N$ customers in the system $\Prob(N)$  is

@@

In a tandem queueing network, customers traverse an ordered series of queues before departing the system. Real examples of such systems include airport terminals, internet services and manufacturing systems. In a parallel network, customers are partitioned into different $\mathbf{(a,s)}$ to be seen by separate queueing systems. In a fork/join network a task (another term for customer) is forked into a number of subtasks which are to be completed by distinct parallel servers. The difference from the parallel network is that the task can only depart the system once all subtasks have arrived at the join point.

@@

\begin{figure}[!htb]
\centering
\includegraphics[width = 0.8\textwidth]{Figures/queuelength_dplyr.pdf}
\caption{Queue lengths over the course of the day for ``manual" and ``smart gate" immigration routes. }
\label{fig:queuelength_dplyr}
\end{figure}

>>>>

In the case of a $M/M/K$, system equilibrium distributions for performance measures can be derived analytically. These derivations are found in standard queueing theory textbooks \citep{lipsky2008queueing, thomopoulos2012fundamentals}. For instance, the limit probability of $N$ customers in the system $\Prob(N)$  is

@@

In a tandem queueing network, customers traverse an ordered series of queues before departing the system. Real examples of such systems include airport terminals, internet services and manufacturing systems. In a parallel network, customers are partitioned into different queueing systems, with their own two vectors $\mathbf{a}$ and $\mathbf{s}$. In a fork/join network a task (another term for customer) is split into a number of subtasks which are to be completed by distinct parallel servers. The task is only complete once all its associated subtasks arrive at the join point. One example of this situation is that of arriving passengers and their bags at an airport.

The difference from the parallel network is that the task can only depart the system once all its associated subtasks have arrived at the join point.

@@

\begin{figure}[!htb]
\centering
\includegraphics[width = 0.75\textwidth]{Figures/queuelength_dplyr.pdf}
\caption{Queue lengths over the course of the day for ``manual" and ``smart gate" immigration routes. }
\label{fig:queuelength_dplyr}
\end{figure}
